TO FIND

### 2013-05-17 ms.tex
Results fig 2

In fig. 2,

>>>>

In fig. 2, we present the richness of each node of the network, as a function of
the centrality of the node, under different assumptions of meta-community
dynamics and network structure. It appears that both in the goeographical and
tree graph, the path dynamics model allows more diversity to persist overall.
However, the local diversity increases with the node centrality, whether it is
measured by the degree or the eigencentrality. All situations examined give a
remarkably congruent signal. The patch dynamics model, \emph{i.e.} when there
are no interactions between species, allows more $\alpha$ diversity. The neutral
model allowed the maintenance of slightly more diversity than the
species-sorting model. In all cases however, it is clear that the richness
maintained tend to increase with the node centrality.
